RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-04-28 inst/doc/pubs/manuscript.Rmd

---
layout: preprint
#layout: review, 11pt
title: "RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Hilmar Lapp
    affiliation: NESCent
  - name: Scott Chamberlain
    affiliation: SimonFraser
  - name: Rutger Vos
    affiliation: NBC
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: NESCent
    address: | 
      National Evolutionary Synthesis Center, Durham, NC, USA
  - code: SimonFraser
    address: |
      Department of Biology, Simon Fraser University, Burnaby, Canada
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
abstract: | 
      1. NeXML promises to be the next generation of phylogenetic
      informatics data and metadata exchange formats, offering substantial
      improvements in reliability, extensibility, and richness over
      earlier standards such as NEXUS.

      2. In this paper we present the RNeXML package, which provides
      a bridge between this rich and reliable data format and the
      extensive library of phylogenetic tools already available in R,
      with a particular emphasis on comparative methods.

      3. RNeXML allows R users to both read and write NeXML files. Yet
      RNeXML is much richer than a basic parser: here we illustrate
      how the package facilitates adding and manipulating semantic 
      annotations.

      4. An essential feature of NeXML is to provide both the flexibility
      to be continually extended to meet the emerging needs of the phylogenetics
      community while remaining backwards-compatible with software developed
      for earlier versions.  Here we illustrate how RNeXML makes it easy
      to extend NeXML in this way.

      5. RNeXML is perfectly suited for users to preserve and maintain their
      personal archives of phylogenetic and comparative trait data in consistent,
      query-able, and cross-platform format, or leverage the rapidly growing 
      public community archives of rich NeXML files.

>>>>

---
layout: preprint
#layout: review, 11pt
title: "RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Hilmar Lapp
    affiliation: NESCent
  - name: Scott Chamberlain
    affiliation: SimonFraser
  - name: Rutger Vos
    affiliation: NBC
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: NESCent
    address: | 
      National Evolutionary Synthesis Center, Durham, NC, USA
  - code: SimonFraser
    address: |
      Department of Biology, Simon Fraser University, Burnaby, Canada
  - code: NBC
    address: | 
      Naturalis Biodiversity Center, Leiden, the Netherlands
abstract: | 
      1. NeXML promises to be the next generation of phylogenetic
      informatics data and metadata exchange formats, offering substantial
      improvements in reliability, extensibility, and richness over
      earlier standards such as NEXUS. In this paper we present the RNeXML
      package which provides a bridge between this rich and reliable
      data format and the extensive library of phylogenetic tools already
      available in R, with a particular emphasis on comparative methods.

      2. In this paper we present the RNeXML package, which provides
      a bridge between this rich and reliable data format and the
      extensive library of phylogenetic tools already available in R,
      with a particular emphasis on comparative methods. 
      RNeXML is much richer than a basic parser: here we illustrate
      how the package facilitates adding and manipulating semantic 
      annotations.

      3. An essential feature of NeXML is to provide both the flexibility
      to be continually extended to meet the emerging needs of the phylogenetics
      community while remaining backwards-compatible with software developed
      for earlier versions.  Here we illustrate how RNeXML makes it easy
      to extend NeXML in this manner.

      4. RNeXML is perfectly suited for users to preserve and maintain their
      personal archives of phylogenetic and comparative trait data in consistent,
      query-able, and cross-platform format, or leverage the rapidly growing 
      public community archives of rich NeXML files.
